### 2021-07-02 analysis/analysis.tex
Updates

\documentclass[usenames,dvipsnames,acmsmall]{acmart}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[nounderscore]{syntax}
\usepackage{bussproofs}
\usepackage{mathtools}

\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{minted}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{minted}

@@

>>>>

\documentclass[usenames,dvipsnames,acmsmall]{acmart}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[nounderscore]{syntax}
\usepackage{bussproofs}
\usepackage{mathtools}
\usepackage[ruled,lined,linesnumbered]{algorithm2e}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{minted}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{minted}

@@

\section{PSE Approach}
\begin{itemize}
	\item Get the path contraints from KLEE, encoding each one into a \textsc{SMT} formula.
	\item \ A single \textit{abstract} path may have multiple \textit{randomized} runs, each corresponding to a different \textit{setting} of the \textit{probabilistic} variables.
	\item For each of the path $\in$ \textit{abstract program paths}, 
	\begin{itemize}
		\item We treat the \textit{probabilistic} variables as \textit{nondet} vars.
		\item Find the estimated \textsc{Expected} value of the \textit{probabilistic} variable.
		\item For each of the \textit{probabilistic} run record the setting of for the \textit{forall} variable. 
		\item We use these as \textit{forall} inputs later for the \textit{concrete} runs.
		\item The constraints for each run is encoded into a \textit{smt} formula. We make one call to \textsc{Z3} at the end to get the value for all the randomized runs. 
		\item The \textsc{Expected} value will be an estimation here, we choose say the top \textit{k} candidates only, reposnsible for  \textit{maximizing} $\sum_{1}^{k} w_{i}$ (Total Mass Probability).
	\end{itemize}
	\item Now we do concrete runs of the program multiple times using the \textit{forall} variable values from \textit{randomized} runs.
	\item We use a \textit{path} selection heuristic using a \textit{maximizing} value of the \textsc{forall} setting that leads to a \textit{violation}.	
\end{itemize}
